---
title: "covid 19"
author: "Michelle Benavides"
date: "July 21, 2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

Examining the table, it seems as though more men have died in this study as compared to females (44 males compared to 25 females). Additionally, there seems to be more females in the sample of the study (1831) compared to males in the sample (1411); this would suggest that a higher proportion of men died in this study compared to the women in this study, but further testing is required to confirm whether this difference in proportion is statistically significant. 

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

When considering the frequency-based ggplot bar chart computed, it appears that there are about 1800 living females in the study, and around 1400 living males. However, more male persons were reported as dead than females, while there were a couple hundred more females in the study sample as a whole. According to the bar char, the majority of the reported deaths were indicated as male. Further tests are required, perferablly with a numerical test. 

  
## Numerical results


## Inferential results 




## Conclusions

